---
title: "EDA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, load_packages}
library(tidyverse)
library(reshape2)
library(matrixStats)
library(GGally)
```

```{r, read-in}

data_url <- 'https://raw.githubusercontent.com/jyurko/INFSCI_2595_Spring_2021/main/HW/final_project/infsci_2595_s21_final_project_data.csv'

df <- readr::read_csv(data_url, col_names = TRUE)
```

```{r, glimpse}
df %>% glimpse()
```

Check for missing values in the data-set

```{r}
visdat::vis_miss(df)
```
There are no missing values in the data-set

Visualizing the type of data in the data-set

```{r, data_types}

visdat::vis_dat(df)

```
xA, xB and outcome_2 are character type data. While all the other fields are numeric. 

No. of unique values in the  variables in the data

```{r, Unique_vals}

df %>% purrr::map_dbl(~length(unique(.)))

```

Looking at the first few values of the data-set

```{r, df_head}

head(df)

```

Separating variables associated with Option A classification formulation.

```{r}
df_A <- df %>% select(xA, xB, x01:x11, outcome_2) %>%
  mutate(outcome_2 = factor(outcome_2, levels = c("Fail", "Pass")))

df_A %>% glimpse()
```



Count of different values under xA:

```{r}
#Bar plots for xA
df %>% ggplot(mapping = aes(x = xA))+
  geom_bar(width = 0.5)+
  geom_text(stat = 'count', aes(label = ..count..), vjust = 0)
```

Count of different values under xB:

```{r}
#Bar plots for xA
df %>% ggplot(mapping = aes(x = xB))+
  geom_bar(width = 0.5)+
  geom_text(stat = 'count', aes(label = ..count..), vjust = 0)
```




```{r, univariate analysis}
summary(df)
```

```{r, range}
#Finding the range for convenience

conti_var <- df %>%   #Data-set with all continuous inputs
  select(x01:x11, response_1)

for (i in 1:ncol(conti_var)){
  print(paste0(colnames(conti_var[i]), " : ", max(conti_var[,i])-min(conti_var[,i]) ))
}
```


```{r, analyzing continuous variables, histogram}

conti_var %>% 
  tibble::rowid_to_column() %>% 
  pivot_longer(!rowid) %>%
  ggplot(mapping = aes(x = value))+
  geom_histogram(bins = 35)+
  facet_wrap(~name, scales = "free")
```

The continuous variables are predominantly Gaussian, hence there is no need to apply transformations. 


```{r, box-plots}
df_A %>% 
  ggplot(mapping = aes(y = x01))+
  geom_boxplot()+
  facet_grid(xA~xB)
```

```{r}
df_A %>% 
  ggplot(mapping = aes(y = x02))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x03))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x04))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x05))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x06))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x07))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x08))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x09))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x10))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df_A %>% 
  ggplot(mapping = aes(y = x11))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
```{r}
df %>% 
  ggplot(mapping = aes(y = response_1))+
  geom_boxplot()+
  facet_grid(xA~xB)

```
It can be inferred from the above plots that there are no differences between the input values as well as response_1 based on the discrete groups.

Correlation plot for continous inputs

```{r, correlation}
df_A %>%
  purrr::keep(is.numeric) %>%
  cor() %>%
  corrplot::corrplot(type = 'upper', method = 'square')

```

It can be seen that the continuous inputs are not correlated.

```{r}
df %>% select (response_1, x01,x02,x03,04,x05,x06) %>%
  cor() %>%
  corrplot::corrplot(type = 'upper', method = 'square')

```
It can be seen that response_1 is highly correlated to x01 and x02.


```{r}
df2 <- df %>%
  mutate(y = ifelse(outcome_2 == 'Fail', 1,0))
```

Shown below is the visualization of outcome_2 wrt response_1

```{r}
df2 %>%
  ggplot(mapping = aes(x = response_1, y = y))+
  geom_point()+
  geom_smooth(method = "glm", family = 'binomial', formula = y ~ splines::ns(x,2))

```
Now visualizing the behavior between Step 2 inputs and outcome_2

```{r}
df2 %>%
  ggplot(mapping = aes(x = x07, y = y))+
  geom_point()+
  geom_smooth(method = "glm", family = 'binomial', formula = y ~ splines::ns(x,2))
```


```{r}
df2 %>%
  ggplot(mapping = aes(x = x08, y = y))+
  geom_point()+
  geom_smooth(method = "glm", family = 'binomial', formula = y ~ splines::ns(x,2))


```


```{r}
df2 %>%
  ggplot(mapping = aes(x = x09, y = y))+
  geom_point()+
  geom_smooth(method = "glm", family = 'binomial', formula = y ~ splines::ns(x,2))

```

```{r}
df2 %>%
  ggplot(mapping = aes(x = x10, y = y))+
  geom_point()+
  geom_smooth(method = "glm", family = 'binomial', formula = y ~ splines::ns(x,2))

```


```{r}
df2 %>%
  ggplot(mapping = aes(x = x11, y = y))+
  geom_point()+
  geom_smooth(method = "glm", family = 'binomial', formula = y ~ splines::ns(x,2))

```

